Dual terminal sliding mode control

### 2016-05-15 paper3_manuscript.tex
20160514
20160515

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.

@@

\subsection{Performance of the robot manipulator}
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}

>>>>

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically. For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.

@@

and one can produce a MDSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:
\Vert g_1(x,t)\Vert &= \Vert 0.1\sin(20t)\Vert\le 0.1\\
\Vert g_2(x,t)\Vert &= \Vert 0.3\sin(3t)+0.5e^{-3t}\Vert\le 0.8,
and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$. Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly. The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $\eta = 20$. Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly. Therefore the design of the MDSM controller for the system~(\ref{eq:simulation four order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par
From Figure~\ref{Figure:2}, it's apparent that the states converge to their desired states. Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the largely chattering caused by $\eta$, the saturation function $sat()$ is applied to take place of $sign()$ to absorb it. Also, although the states have be adjusted to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range. The nature of the situation mention above is the input compensating the error caused by the distance.\par
At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robot manipulator directly.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig2.eps}
\caption{1}
\label{Figure:2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig3.eps}
\caption{2}
\label{Figure:3}
\end{figure}
\subsection{Performance of the robot manipulator}
In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following context. Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{paper3_fig1.eps}
\caption{2}
\label{Figure:1}
\end{figure}

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{2}
\label{Figure:5}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{2}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{2}
\label{Figure:7}
\end{figure}
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}
